Tidal field anisotropy as a tracer of cosmic voids

### 2015-02-13 cosmic_voids.tex
fixed some typos

%.........................................................................
\subsubsection{Velocity profiles}
\label{subsubsec:velocity_voids}
%.........................................................................

@@

We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.
For voids with sizes $r_{\rm eff}<8$\hMpc the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

%.........................................................................
\subsubsection{FA profiles}
\label{subsubsec:FA_voids}
%.........................................................................

>>>>

%.........................................................................
\subsection{Velocity profiles}
\label{subsec:velocity_voids}
%.........................................................................

@@

We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.
For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

%.........................................................................
\subsection{Fractional Anisotropy profiles}
\label{subsec:FA_voids}
%.........................................................................
